CRUSE to Safe Cycling in Ireland \\\large{An Open Source Tool to Support Active Travel}

### 2023-10-10 paper.qmd
Blinded review version

# # Uncomment for draft versions:
format: 
  # html: default
  # docx: default
# Uncomment for formatted version
  elsevier-pdf:
    linestretch: 2
    keep-tex: true
    journal:
      name: European Transport Research Review
      formatting: preprint
      model: 3p
      cite-style: super
# # #   # pdf: default

# # Uncomment the following line to produce the cover page
author:
  - name: Robin Lovelace
    email: r.lovelace@leeds.ac.uk
    corresponding: true
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
  - name: Joey Talbot
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
  - name: Eugeni Vidal-Tortosa
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
  - name: Hussein Mahfouz
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
  - name: Elaine Brick
    affiliations:
      - name: AECOM
        address: Unit 6, Galway Technology Park, Parkmore, Galway, Ireland
  - name: Peter Wright
    affiliations:
      - name: AECOM
        address: Winslade House, Winslade Park, Manor Drive, Clyst St Mary, Exeter, EX5 1FY, UK
  - name: "Gary O'Tool"
    affiliations:
      - name: AECOM
        address: Unit 6, Galway Technology Park, Parkmore, Galway, Ireland
  - name: Dan Brennan
    affiliations:
      - name: Transport Infrastructure Ireland
        address: Parkgate Business Centre, Parkgate Street, Dublin 8, D08 DK10, Ireland
  - name: Suzanne Meade
    affiliations:
      - name: Transport Infrastructure Ireland
        address: Parkgate Business Centre, Parkgate Street, Dublin 8, D08 DK10, Ireland
abstract: |
  Legislation mandates improved road safety and decarbonisation of predominantly road-based transport network in Ireland and other countries. The Cycle Route Uptake and Scenario Estimation (CRUSE) Tool was commissioned to support cycle network planning, safety interventions, business case development and project evaluation.
  Cycling in Ireland represents only 3% of total modal share as of the latest Census (2016), but accounts for 20% of serious injuries and 7% of all fatalities.
  High resolution datasets on baseline and potential cycling levels are needed to meet Ireland's climate and safety targets.

>>>>

# # Uncomment for draft versions:
format: 
  html: default
  # docx: default
# Uncomment for formatted version
  elsevier-pdf:
    linestretch: 2
    keep-tex: true
    journal:
      name: European Transport Research Review
      formatting: preprint
      model: 3p
      cite-style: super
# # #   # pdf: default

# # # Uncomment the following line to produce the cover page
# author:
#   - name: Robin Lovelace
#     email: r.lovelace@leeds.ac.uk
#     corresponding: true
#     affiliations:
#       - name: University of Leeds
#         address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
#   - name: Joey Talbot
#     affiliations:
#       - name: University of Leeds
#         address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
#   - name: Eugeni Vidal-Tortosa
#     affiliations:
#       - name: University of Leeds
#         address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
#   - name: Hussein Mahfouz
#     affiliations:
#       - name: University of Leeds
#         address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
#   - name: Elaine Brick
#     affiliations:
#       - name: AECOM
#         address: Unit 6, Galway Technology Park, Parkmore, Galway, Ireland
#   - name: Peter Wright
#     affiliations:
#       - name: AECOM
#         address: Winslade House, Winslade Park, Manor Drive, Clyst St Mary, Exeter, EX5 1FY, UK
#   - name: "Gary O'Tool"
#     affiliations:
#       - name: AECOM
#         address: Unit 6, Galway Technology Park, Parkmore, Galway, Ireland
#   - name: Dan Brennan
#     affiliations:
#       - name: Transport Infrastructure Ireland
#         address: Parkgate Business Centre, Parkgate Street, Dublin 8, D08 DK10, Ireland
#   - name: Suzanne Meade
#     affiliations:
#       - name: Transport Infrastructure Ireland
#         address: Parkgate Business Centre, Parkgate Street, Dublin 8, D08 DK10, Ireland
abstract: |
  Legislation mandates improved road safety and decarbonisation of predominantly road-based transport network in Ireland and other countries. The Cycle Route Uptake and Scenario Estimation (CRUSE) Tool was commissioned to support cycle network planning, safety interventions, business case development and project evaluation.
  Cycling in Ireland represents only 3% of total modal share as of the latest Census (2016), but accounts for 20% of serious injuries and 7% of all fatalities.
  High resolution datasets on baseline and potential cycling levels are needed to meet Ireland's climate and safety targets.

### 2023-10-10 paper.tex
Blinded review version

\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\journal{European Transport Research Review}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-num}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={CRUSE to Safe Cycling in Ireland},
  pdfauthor={Robin Lovelace; Joey Talbot; Eugeni Vidal-Tortosa; Hussein Mahfouz; Elaine Brick; Peter Wright; Gary O'Tool; Dan Brennan; Suzanne Meade},
  pdfkeywords={Cycling, Open-source, Road Safety, Active Travel},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{frontmatter}
\title{CRUSE to Safe Cycling in Ireland \\\large{An Open Source Tool to
Support Active Travel} }
\author[1]{Robin Lovelace%
\corref{cor1}%
}
 \ead{r.lovelace@leeds.ac.uk} 
\author[1]{Joey Talbot%
%
}

\author[1]{Eugeni Vidal-Tortosa%
%
}

\author[1]{Hussein Mahfouz%
%
}

\author[2]{Elaine Brick%
%
}

\author[3]{Peter Wright%
%
}

\author[2]{Gary O'Tool%
%
}

\author[4]{Dan Brennan%
%
}

\author[4]{Suzanne Meade%
%
}

\affiliation[1]{organization={University of
Leeds},addressline={Institute for Transport Studies, Leeds, LS2 9JT,
United Kingdom},postcodesep={}}
\affiliation[2]{organization={AECOM},addressline={Unit 6, Galway
Technology Park, Parkmore, Galway, Ireland},postcodesep={}}
\affiliation[3]{organization={AECOM},addressline={Winslade House,
Winslade Park, Manor Drive, Clyst St Mary, Exeter, EX5 1FY,
UK},postcodesep={}}
\affiliation[4]{organization={Transport Infrastructure
Ireland},addressline={Parkgate Business Centre, Parkgate Street, Dublin
8, D08 DK10, Ireland},postcodesep={}}

@@

\begin{keyword}
    Cycling \sep Open-source \sep Road Safety \sep 
    Active Travel
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, enhanced, interior hidden, breakable, frame hidden]}{\end{tcolorbox}}\fi

>>>>

\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\journal{European Transport Research Review}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-num}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={CRUSE to Safe Cycling in Ireland},
  pdfkeywords={Cycling, Open-source, Road Safety, Active Travel},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{frontmatter}
\title{CRUSE to Safe Cycling in Ireland \\\large{An Open Source Tool to
Support Active Travel} }

@@

\begin{keyword}
    Cycling \sep Open-source \sep Road Safety \sep 
    Active Travel
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, interior hidden, enhanced, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, sharp corners, frame hidden]}{\end{tcolorbox}}\fi
